Predicting which anime are animazing through quantitative analysis

### 2024-04-14 paper/paper.qmd
Rendered paper

---
title: "Predicting which anime are animazing through quantitative analysis"
subtitle: "People are more likely to rate great anime, regardless of age"
author: Allen Uy
thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
date: today
date-format: long
abstract: "This paper examines the top 10000 anime on MyAnimeList (MAL) by user score to understand the tendencies of highly rated anime. Using data provided by the MAL API, we discovered that the fraction of users that rate an anime to the total users that have engaged with the anime is a large indicator of user score. Our multiple linear regression model predicts the user score of an anime based on scoring fraction, date, and popularity and may indicate highly rated anime that have not yet gotten adequate exposure based on difference between the predicted and actual scores. This concept of scoring fraction is applicable to media forms beyond anime and may serve as the basis for recommendation algorithms."
format: pdf
number-sections: true
bibliography: references.bib
keywords: anime, regression, MyAnimeList
---

@@

@@

my_fmt <- list(
  intercept = list(fmt = "%.2f"),
  fraction = list(fmt = "%.2f"),
  days_since_start = list(fmt = "%#.2e"),
  num_list_users = list(fmt = "%#.2e")
)

table <- modelsummary(
  model,
  statistic = "mad",
  fmt = my_fmt,
  output = "kableExtra"
)

@@

predictions <- clean_anime |>
  filter(!is.na(fraction) & !is.na(num_list_users) & !is.na(days_since_start)) |>
  mutate(predicted = predict(model, .)) |>
  select(title, rank, popularity, mean, num_list_users, fraction, start_date, days_since_start, predicted)

bind_rows(head(predictions, 5), tail(predictions, 5)) |>
  select(id, title, rank, start_date, studio, mean, popularity, num_list_users,
         num_scoring_users, adventure, drama, fraction, days_since_start) |>
  kable(
    booktabs = TRUE,
    linesep = ""
  ) |> kable_styling(latex_options = "scale_down")
```

>>>>

---
title: "Predicting which anime are animazing through quantitative analysis"
subtitle: "People are more likely to rate great anime, regardless of age"
author: Allen Uy
thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
date: today
date-format: long
abstract: "This paper examines the top 10000 anime on MyAnimeList (MAL) by user score to understand the tendencies of highly rated anime. Using data provided by the MAL API, we discovered that the fraction of users that rate an anime to the total users that have engaged with the anime is a large indicator of user score. Our multiple linear regression model predicts the user score of an anime based on scoring fraction, date, and popularity and may indicate highly rated anime that have not yet gotten adequate exposure based on difference between the predicted and actual scores. This concept of scoring fraction is applicable to media forms beyond anime and may serve as the basis for recommendation algorithms."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Can I add keywords under abstract somehow? keywords: anime, regression, MyAnimeList

@@

table <- modelsummary(
  model,
  statistic = "mad",
  fmt = fmt_sprintf("%.3e"),
  output = "kableExtra"
)

@@

predictions <- clean_anime |>
  filter(!is.na(fraction) & !is.na(num_list_users) & !is.na(days_since_start)) |>
  mutate(predicted = predict(model, .)) |>
  select(title, rank, popularity, num_list_users, fraction, start_date, days_since_start, mean, predicted)

bind_rows(head(predictions, 5), tail(predictions, 5)) |>
  kable(
    booktabs = TRUE,
    linesep = ""
  ) |> kable_styling(latex_options = "scale_down")
```
